---
title: "Assignment9"
author: "Ryan Weber"
date: "April 1, 2018"
output: 
  html_document:
    theme: lumen
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(httr)
library(purrr)
library(magrittr)
library(listviewer)
library(stringr)
library(lubridate)
library(dplyr)

api_key <- read.table(file = "/Users/ryanweber/Desktop/CUNY/Data 607 Db/Assignments/Week 9/api_key.txt", stringsAsFactors = FALSE)[1, 1]
```

# How many of the Oscar foreign film nominees were reviewed by the NY Times as 'Critic's Picks' (2010-2015)

github: https://github.com/rweberc/Data607_Assignment9

### Get Critic's Picks reviews for the past 5 years
```{r}
reviewDf <- NULL

getReviews <- function(offset){
  # Create URL
  url <- str_c("https://api.nytimes.com/svc/movies/v2/reviews/search.json?critics-pick=Y&api-key=", 
               api_key, "&offset=", offset)
  
  # Get content
  reviewList <- content(GET(url), "parse")
  
  # Parse relevant fields to df
  reviewList$results %>% map_df(extract, c('display_title', 'publication_date'))
}

# Retrieve Critics Picks for the past 5 years #940
titlesList <- map(seq(340,1400, 20), getReviews)

#jsonedit(titlesList)

titleDf <- map_df(titlesList, extract)

# Filter publication date from 2013 to 
titleDf$publication_date <- ymd(titleDf$publication_date)
summary(titleDf$publication_date)
titleDf <- titleDf %>% filter(year(publication_date) >= 2010 & year(publication_date) <= 2015)

head(titleDf)
```

### Read in database of Oscar nominees and winners
```{r}
oscarDf <- read.csv("https://raw.githubusercontent.com/rweberc/Data607_Assignment9/master/database.csv", 
                    stringsAsFactors = FALSE)

# Parse year and select columns of interest
oscarDf$Year <- str_replace(oscarDf$Year, "/.*", "")

oscarDf$Year <- as.numeric(oscarDf$Year)

oscarDf <- oscarDf %>% 
  filter(Year >= 2010 & Year <= 2015) %>%
  select(Film, Name, Year, Award, Winner)

foreignDf <- oscarDf %>%
  filter(Award == "Foreign Language Film")
  

head(foreignDf)
```

### Compare results
```{r}
foreignCriticPickDf <- inner_join(foreignDf, titleDf, by=c("Name"="display_title"))

foreignCriticPickDf
```

Only 2 out of 30 Foreign Language Film nominees look to have been Critic's Picks.

### How about Oscar winners overall?
```{r}
winnerDf <- oscarDf %>%
  filter(Winner == 1)

# Film name in database is sometimes in different
winnerCriticPickDf1 <- inner_join(winnerDf, titleDf, by=c("Film"="display_title")) 
winnerCriticPickDf2 <- inner_join(winnerDf, titleDf, by=c("Name"="display_title"))

winnerCriticPickDf <- bind_rows(winnerCriticPickDf1, winnerCriticPickDf2)

head(winnerCriticPickDf)
```

Only 6 out of 74 Oscar winners overall were Critic's Picks.

The low numbers make me wonder if there is some assumption I missed.  Could possibly lose some cases due to special character differences between the two datasets.

Not sure if this is really an indication that the Oscars are missing important movies or if the Critics Picks are.

Could compare these against a more reputable international film award source to try to get a sense of that.